Incentivizing Exploration with Unbiased History

### 2018-10-31 2level.tex
Moved Greedy into Warmup, and started revising.

%!TEX root = main.tex
\section{Warm-up:  2-Level Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists of two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
  rounds. This is done by dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and allowing each agent to only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

>>>>

%!TEX root = main.tex
\section{Warm-up: Explore-then-Exploit Policy}

We first consider the simplest disclosure policy which reveals the full history in each round $t$, \ie $m_t=\SubH{t-1}$; we call it the \emph{full-disclosure policy}. The info-path for this policy is a simple path. We use this policy as a ``gadget" in our constructions. Hence, we formulate it slightly more generally:

\begin{definition}
A subset of rounds $S\subset [T]$ is called a \emph{full-disclosure path} in info-graph $G$ if the induced subgraph $G_S$ is a simple path, and it connects to the rest of the graph only through the terminal node $\max(S)$, if at all.
\end{definition}

We prove that with constant probability, a full-disclosure path of constant length samples each arm at least once (and we will build on this fact throughout).

\ascomment{stopped here.}

\begin{lemma}
\label{lem:greedy}
Under Assumption \ref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability
at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least
once.\footnote{The notations $O_k$ and $\Omega_K$ hide the dependence
  on the number of arms $K$.} \nicomment{If we change the name of the policy, we might also want to change the subscripts of these constants.}
\end{lemma}

\begin{proof}
  Fix any arm $a$. Let $\GdT = (K-1) \cdot c_T + 1$ and
  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
    all the realized rewards in $\GdT$ rounds are 0, which occurs with
    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
  In this case, we want to show that arm $a$ is pulled at least
  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
  the pigeonhole principle, we know that there is some other arm $a'$
  that is pulled at least $c_T + 1$ rounds. Let $t$ be the round in
  which arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption
  \ref{ass:embehave}, we know
  \[
    \hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3.
  \]
  \nicomment{Wait, where did we set $c_T$?} On the other hand, we have
  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
  \swdelete{ In addition, we know that this case happens with
    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
    at most $2/3$. To sum up, we know that with probability at least
    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
   \jmcomment{Agree with these changes.}
\end{proof}

\swedit{In our policies presented in the next sections, we will use
  \ALGG of $T_G$ rounds as a subroutine for initial exploration. For
  any $a$, let $q_a$ \nicomment{$q$ sounds like a fraction; maybe $n^G_a$ or $N^G_a$} be the expected number of arm $a$ pulls in one
  run of \ALGG of $T_G$ rounds.} \nicomment{\ALGG of $T_G$ rounds is a mouthful; what about using notation like \ALGG($T_G$)? or if we will always use $T_G$ rounds, then just define the policy to be that from now on?}

\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists of two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
  rounds. This is done by dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and allowing each agent to only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.
